MSOA domestic Electricty and Gas maps

### 2021-08-09 MSOA domestic Elec and Gas.Rmd
Pushing again

```{r Mapping the change in dom mean gas comsumption}
merged_domgas$MSOA11CD <- merged_domgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
ggplot2::ggplot(msoa_domgas20102019) +
  geom_sf(aes(fill=mc_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```

>>>>

```{r Mapping the change in dom mean gas comsumption}
merged_domgas$MSOA11CD <- merged_domgas$"Middle Layer Super Output Area (MSOA) Code" #creating a variable with the LSOA code in the same name as in sf_data
msoa_domgas20102019 <- merge(msoa_sf_data, merged_domgas) #merging these
ggplot2::ggplot(msoa_domgas20102019) +
  geom_sf(aes(fill=mc_diff))+ 
  scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  labs(caption ="Solent (all MSOAs)")
```
##END
